My title\thanks{Code and data are available at: {[}https://github.com/wyx827/2024USpresidentialelection.git{]}.}

### 2024-10-23 paper/paper.qmd
Update model section and make prediction.

```{r}
library(tidyverse)
library(ggplot2)
analysis_data <- read_csv(here::here("data/02-analysis_data/cleaned_US_voting.csv"))
```

@@

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

@@

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

@@

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Logistic Regression Model Build up

To predict whether Donald Trump would win over Kamala Harris based on polling data, we constructed a logistic regression model using a subset of 1,000 randomly sampled observations from our cleaned dataset. The dependent variable, trump_win, is a binary outcome representing whether Trump was predicted to win in a given state (1 for Trump win, 0 for Harris win). The independent variables included in the model are pollster_rating_name, state, population_group, numeric_grade, sample_size, and methodology.

We used the logit link function given that our outcome variable is binary. The logistic regression model estimates the log odds of Trump winning as a linear function of these predictors. Each predictor variable was selected based on its relevance to polling outcomes:

	•	pollster_rating_name captures the credibility of the polling firm, as rated by independent organizations.
	•	state accounts for geographic variations in voter preferences.
	•	population_group represents different demographic categories.
	•	numeric_grade reflects the poll’s quality rating.
	•	sample_size measures the size of the poll’s sample, which can impact the poll’s reliability.
	•	methodology captures how the poll was conducted (e.g., online, phone-based, etc.).

We applied a Bayesian approach to estimate the logistic regression model using Stan, with weakly informative priors (Normal distribution with mean 0 and standard deviation 2.5) for both the coefficients and the intercept. These priors reflect our assumption that the effect of each predictor is centered around 0, with a moderate level of uncertainty.
By incorporating state and demographic information along with pollster quality and methodology, we aim to capture the variability in polling predictions across different regions and polling practices. The use of Bayesian inference allows us to quantify uncertainty in our predictions more effectively.

We use weakly informative Normal priors for the intercept ( \alpha ) and coefficients ( \beta_i ), centered around zero with a standard deviation of 2.5. These priors were chosen to allow the data to influence the predictions while still reflecting reasonable uncertainty. Specifically:

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_{i} &\sim \mbox{Normal}(0, 2.5) \\
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

```{r}
logistic_model <- readRDS(here::here(("models/logistic_model.rds")))
```

# Diagnostic plots for the MLR model
par(mfrow = c(2, 2))
plot(mlr_harris_model)
par(mfrow = c(1, 1))  # Reset plot layout

@@

Our results are summarized in ...

```{r}

library(rstanarm)

first_model <-
  readRDS(file = (here::here("models/logistic_model.rds")))
```

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

>>>>

```{r}
#install.packages("tidymodels")
library(tidyverse)
library(ggplot2)
analysis_data <- read_csv(here::here("data/02-analysis_data/cleaned_US_voting.csv"))
```

@@

We use the statistical programming language R [@citeR].... Following @tellingstories, we consider...

@@

Some of our data is of penguins (@fig-bills),

@@

To model Donald Trump’s polling percentages over time, we employed a Bayesian linear regression framework. Bayesian methods provide a flexible approach to inference by incorporating prior beliefs and updating them with observed data, allowing us to quantify uncertainty in both parameter estimates and predictions.

Here we briefly describe the Bayesian model used to investigate the winning probability of Trump. Background details and diagnostics are included in [Appendix -@sec-model-details].

## Multiple Linear Regression Model Overview
The model now predicts Trump’s polling percentage (percent) using the following predictors:

- Numeric Grade (numeric_grade): Reflects the quality rating of the pollster.
- Sample Size (sample_size): The number of respondents in the poll.
- State (state): A categorical variable for different U.S. states.
- Transparency Score (transparency_score): A measure of how transparent the polling data and methodology are.
- End Date (end_date): The date the poll was completed, which might capture trends over time.

The model takes the form:
The model takes the form:

# #Interpretation of Coefficients:

- Intercept (\beta_0): This is the predicted Trump polling percentage when all predictors (numeric grade, sample size, state, transparency score, and end date) are at their baseline or zero value.
- Numeric Grade (\beta_1): This coefficient measures how much Trump’s polling percentage changes as the pollster’s numeric grade increases. A positive and significant coefficient would indicate that higher-rated pollsters report better polling numbers for Trump, while a negative coefficient would suggest the opposite.
- Sample Size (\beta_2): This measures the impact of the number of respondents on Trump’s polling percentage. A positive coefficient would indicate that larger sample sizes are associated with higher polling percentages for Trump.
- State (\beta_3): The coefficients for the state variable represent differences in Trump’s polling percentage in each state compared to the reference state (baseline category). For example, if the coefficient for Florida is negative, it means Trump polls lower in Florida compared to the reference state.
- Transparency Score (\beta_4): This coefficient shows how much Trump’s polling percentage is affected by the transparency of the poll. A positive coefficient would indicate that polls with higher transparency tend to report higher polling percentages for Trump, whereas a negative coefficient would imply the opposite.
- End Date (\beta_5): The end date is a time-related variable, capturing trends over time. A positive and significant coefficient would suggest that Trump’s polling percentage has increased as the election date approaches, while a negative coefficient would suggest a decrease in his polling numbers over time.

## Interpretation
The posterior distributions of the parameters allow us to quantify the uncertainty around each effect:
- The coefficient for end_date informs us about how Trump’s polling percentages have evolved over time. A positive coefficient would suggest an upward trend, while a negative coefficient would indicate a decline.
- The coefficient for numeric_grade captures the impact of pollster quality on the polling percentage. High-quality pollsters may produce different estimates compared to lower-quality ones.
- The state-level effects account for regional differences in Trump’s support. Some states may show significantly higher or lower levels of support, even after adjusting for the time of the poll and pollster quality.

# Model Evalutation
- R-squared
@tbl-summary shows the summary table for the model. And then evaluate it on the test set. It appears as though the model is having difficulty identifying Trump supporters.
```{r}
#| echno: False
#| label: tbl-summary
#| tbl-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

library(knitr)
regression_model<-readRDS(here::here("models/regression_model.rds"))
summary<-summary(regression_model)
# Extract the coefficients (which can be formatted as a table)
coefficients_table <- summary$coefficients

# Display the coefficients table using kable
kable(coefficients_table, digits = 3, caption = "Regression Model Coefficients")
```

# Diagnostic plots for the model
```{r}
#| echno: false
#| label: fig-diagnosis
#| tbl-cap: Linear Regression Assumptions hold.
#| echo: false
#| warning: false
#| message: false

par(mfrow = c(2, 2))  
plot(regression_model)
```

```{r}
library(car)
vif(regression_model)
```

@@

## Predict and Combine with Electroal College to Predict

```{r tbl-prediction, echo=FALSE, warning=FALSE, message=FALSE}
#| echno: false
#| label: tbl-prediction
#| tbl-cap: Prediction for Trump
#| echo: false
#| warning: false
#| message: false

# Define electoral votes for each state
electoral_votes <- data.frame(
  state = c("Alabama", "Alaska", "Arizona", "Arkansas", "California", "Colorado", "Connecticut", "Delaware", "Florida", 
            "Georgia", "Hawaii", "Idaho", "Illinois", "Indiana", "Iowa", "Kansas", "Kentucky", "Louisiana", "Maine", 
            "Maine CD-1", "Maine CD-2", "Maryland", "Massachusetts", "Michigan", "Minnesota", "Mississippi", 
            "Missouri", "Montana", "Nebraska", "Nebraska CD-1", "Nebraska CD-2", "Nebraska CD-3", "Nevada", 
            "New Hampshire", "New Jersey", "New Mexico", "New York", "North Carolina", "North Dakota", "Ohio", 
            "Oklahoma", "Oregon", "Pennsylvania", "Rhode Island", "South Carolina", "South Dakota", "Tennessee", 
            "Texas", "Utah", "Vermont", "Virginia", "Washington", "West Virginia", "Wisconsin", "Wyoming", 
            "District of Columbia"),
  electoral_votes = c(9, 3, 11, 6, 55, 9, 7, 3, 29, 16, 4, 4, 20, 11, 6, 6, 8, 8, 2, 1, 1, 10, 11, 15, 10, 6, 10, 
                      3, 5, 1, 1, 2, 6, 4, 14, 5, 29, 16, 3, 18, 7, 6, 20, 4, 9, 3, 11, 38, 6, 3, 13, 12, 5, 10, 3, 3)
)

# Apply the regression model to predict Trump's percentage in each state
analysis_data$predicted_percent_trump <- predict(regression_model, newdata = analysis_data)

# Summarize Trump's predicted percentage for each state
total_trump <- aggregate(predicted_percent_trump ~ state, data = analysis_data, FUN = mean)

# Join electoral vote data with Trump's predictions
state_predictions <- merge(total_trump, electoral_votes, by = "state")

# Determine the winner for each state based on Trump’s predicted percentage
state_predictions$winner <- ifelse(state_predictions$predicted_percent_trump > 50, "Trump", "Harris")

# Create a table showing the prediction results
library(knitr)
kable(state_predictions, col.names = c("State", "Trump Predicted %", "Electoral Votes", "Winner"),
      digits = 2, caption = "Prediction for Trump by State")
```

@@

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2
library(caret)
library(rstanarm)
library(ggplot2)
library(dplyr)
# Split the data into training (70%) and test (30%) sets
set.seed(853)  # For reproducibility

### 2024-10-23 paper/paper.tex
Model update.
Update model section and make prediction.

\title{My title\thanks{Code and data are available at:
{[}https://github.com/wyx827/2024USpresidentialelection.git{]}.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{First author \and Yongqi Liu \and Yuxuan Wei}
\date{October 22, 2024}

@@

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(tidyverse)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
Rows: 1951 Columns: 10
-- Column specification --------------------------------------------------------
Delimiter: ","
chr  (5): pollster_rating_name, methodology, state, candidate_name, populati...
dbl  (3): numeric_grade, sample_size, percent
date (2): start_date, end_date

@@

We use the statistical programming language R (R Core Team 2023)\ldots.
Our data (Toronto Shelter \& Support Services 2024)\ldots. Following
Alexander (2023), we consider\ldots{}

@@

Some of our data is of penguins (\textbf{?@fig-bills}), from Horst,
Hill, and Gorman (2020).

@@

The goal of our modelling strategy is twofold. Firstly,\ldots{}

Here we briefly describe the Bayesian analysis model used to
investigate\ldots{} Background details and diagnostics are included in
Appendix~\ref{sec-model-details}.

\subsection{Logistic Regression Model Build
up}\label{logistic-regression-model-build-up}

To predict whether Donald Trump would win over Kamala Harris based on
polling data, we constructed a logistic regression model using a subset
of 1,000 randomly sampled observations from our cleaned dataset. The
dependent variable, trump\_win, is a binary outcome representing whether
Trump was predicted to win in a given state (1 for Trump win, 0 for
Harris win). The independent variables included in the model are
pollster\_rating\_name, state, population\_group, numeric\_grade,
sample\_size, and methodology.

We used the logit link function given that our outcome variable is
binary. The logistic regression model estimates the log odds of Trump
winning as a linear function of these predictors. Each predictor
variable was selected based on its relevance to polling outcomes:

\begin{verbatim}
•   pollster_rating_name captures the credibility of the polling firm, as rated by independent organizations.
•   state accounts for geographic variations in voter preferences.
•   population_group represents different demographic categories.
•   numeric_grade reflects the poll’s quality rating.
•   sample_size measures the size of the poll’s sample, which can impact the poll’s reliability.
•   methodology captures how the poll was conducted (e.g., online, phone-based, etc.).
\end{verbatim}

We applied a Bayesian approach to estimate the logistic regression model
using Stan, with weakly informative priors (Normal distribution with
mean 0 and standard deviation 2.5) for both the coefficients and the
intercept. These priors reflect our assumption that the effect of each
predictor is centered around 0, with a moderate level of uncertainty. By
incorporating state and demographic information along with pollster
quality and methodology, we aim to capture the variability in polling
predictions across different regions and polling practices. The use of
Bayesian inference allows us to quantify uncertainty in our predictions
more effectively.

We use weakly informative Normal priors for the intercept ( \alpha ) and
coefficients ( \beta\_i ), centered around zero with a standard
deviation of 2.5. These priors were chosen to allow the data to
influence the predictions while still reflecting reasonable uncertainty.
Specifically:

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta_{i} &\sim \mbox{Normal}(0, 2.5) \\
\end{align}

We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
package of Goodrich et al. (2022). We use the default priors from
\texttt{rstanarm}.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{logistic\_model }\OtherTok{\textless{}{-}} \FunctionTok{readRDS}\NormalTok{(here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{((}\StringTok{"models/logistic\_model.rds"}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

\section{Diagnostic plots for the MLR
model}\label{diagnostic-plots-for-the-mlr-model}

par(mfrow = c(2, 2)) plot(mlr\_harris\_model) par(mfrow = c(1, 1)) \#
Reset plot layout

@@

Our results are summarized in \ldots{}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(rstanarm)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Loading required package: Rcpp
\end{verbatim}

\begin{verbatim}
This is rstanarm version 2.32.1
\end{verbatim}

\begin{verbatim}
- See https://mc-stan.org/rstanarm/articles/priors for changes to default priors!
\end{verbatim}

\begin{verbatim}
- Default priors may change, so it's safest to specify priors, even if equivalent to the defaults.
\end{verbatim}

\begin{verbatim}
- For execution on a local, multicore CPU with excess RAM we recommend calling
\end{verbatim}

\begin{verbatim}
  options(mc.cores = parallel::detectCores())
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{first\_model }\OtherTok{\textless{}{-}}
  \FunctionTok{readRDS}\NormalTok{(}\AttributeTok{file =}\NormalTok{ (here}\SpecialCharTok{::}\FunctionTok{here}\NormalTok{(}\StringTok{"models/logistic\_model.rds"}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

@@

\section*{\# Appendix}\label{appendix}
\addcontentsline{toc}{section}{\# Appendix}

@@

In \textbf{?@fig-ppcheckandposteriorvsprior-1} we implement a posterior
predictive check. This shows\ldots{}

In \textbf{?@fig-ppcheckandposteriorvsprior-2} we compare the posterior
with the prior. This shows\ldots{}

@@

\textbf{?@fig-stanareyouokay-1} is a trace plot. It shows\ldots{} This
suggests\ldots{}

\textbf{?@fig-stanareyouokay-2} is a Rhat plot. It shows\ldots{} This
suggests\ldots{}

@@

\bibitem[\citeproctext]{ref-rstanarm}
Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
{``{rstanarm: {Bayesian} applied regression modeling via {Stan}}.''}
\url{https://mc-stan.org/rstanarm/}.

\bibitem[\citeproctext]{ref-palmerpenguins}
Horst, Allison Marie, Alison Presmanes Hill, and Kristen B Gorman. 2020.
\emph{{palmerpenguins: Palmer Archipelago (Antarctica) penguin data}}.
\url{https://doi.org/10.5281/zenodo.3960218}.

@@

\bibitem[\citeproctext]{ref-shelter}
Toronto Shelter \& Support Services. 2024. \emph{Deaths of Shelter
Residents}.
\url{https://open.toronto.ca/dataset/deaths-of-shelter-residents/}.

>>>>

\title{My title\thanks{Code and data are available at:
{[}https://github.com/wyx827/2024USpresidentialelection.git{]}.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{First author \and Yongqi Liu \and Yuxuan Wei}
\date{October 23, 2024}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#install.packages("tidymodels")}
\FunctionTok{library}\NormalTok{(tidyverse)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
Rows: 1683 Columns: 11
-- Column specification --------------------------------------------------------
Delimiter: ","
chr  (5): pollster_rating_name, methodology, state, candidate_name, populati...
dbl  (4): numeric_grade, sample_size, percent, transparency_score
date (2): start_date, end_date

@@

We use the statistical programming language R (R Core Team 2023)\ldots.
Following Alexander (2023), we consider\ldots{}

@@

Some of our data is of penguins (\textbf{?@fig-bills}),

@@

To model Donald Trump's polling percentages over time, we employed a
Bayesian linear regression framework. Bayesian methods provide a
flexible approach to inference by incorporating prior beliefs and
updating them with observed data, allowing us to quantify uncertainty in
both parameter estimates and predictions.

Here we briefly describe the Bayesian model used to investigate the
winning probability of Trump. Background details and diagnostics are
included in Appendix~\ref{sec-model-details}.

\subsection{Multiple Linear Regression Model
Overview}\label{multiple-linear-regression-model-overview}

The model now predicts Trump's polling percentage (percent) using the
following predictors:

\begin{itemize}
\tightlist
\item
  Numeric Grade (numeric\_grade): Reflects the quality rating of the
  pollster.
\item
  Sample Size (sample\_size): The number of respondents in the poll.
\item
  State (state): A categorical variable for different U.S. states.
\item
  Transparency Score (transparency\_score): A measure of how transparent
  the polling data and methodology are.
\item
  End Date (end\_date): The date the poll was completed, which might
  capture trends over time.
\end{itemize}

The model takes the form: The model takes the form:

\section{\#Interpretation of
Coefficients:}\label{interpretation-of-coefficients}

\begin{itemize}
\tightlist
\item
  Intercept (\beta\_0): This is the predicted Trump polling percentage
  when all predictors (numeric grade, sample size, state, transparency
  score, and end date) are at their baseline or zero value.
\item
  Numeric Grade (\beta\_1): This coefficient measures how much Trump's
  polling percentage changes as the pollster's numeric grade increases.
  A positive and significant coefficient would indicate that
  higher-rated pollsters report better polling numbers for Trump, while
  a negative coefficient would suggest the opposite.
\item
  Sample Size (\beta\_2): This measures the impact of the number of
  respondents on Trump's polling percentage. A positive coefficient
  would indicate that larger sample sizes are associated with higher
  polling percentages for Trump.
\item
  State (\beta\_3): The coefficients for the state variable represent
  differences in Trump's polling percentage in each state compared to
  the reference state (baseline category). For example, if the
  coefficient for Florida is negative, it means Trump polls lower in
  Florida compared to the reference state.
\item
  Transparency Score (\beta\_4): This coefficient shows how much Trump's
  polling percentage is affected by the transparency of the poll. A
  positive coefficient would indicate that polls with higher
  transparency tend to report higher polling percentages for Trump,
  whereas a negative coefficient would imply the opposite.
\item
  End Date (\beta\_5): The end date is a time-related variable,
  capturing trends over time. A positive and significant coefficient
  would suggest that Trump's polling percentage has increased as the
  election date approaches, while a negative coefficient would suggest a
  decrease in his polling numbers over time.
\end{itemize}

\subsection{Interpretation}\label{interpretation}

The posterior distributions of the parameters allow us to quantify the
uncertainty around each effect: - The coefficient for end\_date informs
us about how Trump's polling percentages have evolved over time. A
positive coefficient would suggest an upward trend, while a negative
coefficient would indicate a decline. - The coefficient for
numeric\_grade captures the impact of pollster quality on the polling
percentage. High-quality pollsters may produce different estimates
compared to lower-quality ones. - The state-level effects account for
regional differences in Trump's support. Some states may show
significantly higher or lower levels of support, even after adjusting
for the time of the poll and pollster quality.

\section{Model Evalutation}\label{model-evalutation}

\begin{itemize}
\tightlist
\item
  R-squared Table~\ref{tbl-summary} shows the summary table for the
  model. And then evaluate it on the test set. It appears as though the
  model is having difficulty identifying Trump supporters.
\end{itemize}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2985}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1343}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1642}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1194}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2836}}@{}}

\caption{\label{tbl-summary}Relationship between wing length and width}

\tabularnewline

\caption{Regression Model Coefficients}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Std. Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
t value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Pr(\textgreater\textbar t\textbar)
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Estimate
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Std. Error
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
t value
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Pr(\textgreater\textbar t\textbar)
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
(Intercept) & -67.184 & 14.445 & -4.651 & 0.000 \\
numeric\_grade & 0.914 & 1.006 & 0.909 & 0.364 \\
sample\_size & 0.000 & 0.000 & 0.205 & 0.838 \\
stateArizona & -5.020 & 2.582 & -1.944 & 0.052 \\
stateArkansas & 5.569 & 4.380 & 1.272 & 0.204 \\
stateCalifornia & -18.345 & 2.738 & -6.699 & 0.000 \\
stateColorado & -13.340 & 3.002 & -4.443 & 0.000 \\
stateConnecticut & -13.480 & 3.574 & -3.772 & 0.000 \\
stateFlorida & -3.214 & 2.740 & -1.173 & 0.241 \\
stateGeorgia & -4.814 & 2.573 & -1.871 & 0.062 \\
stateIdaho & 3.467 & 4.379 & 0.792 & 0.429 \\
stateIllinois & -14.064 & 3.275 & -4.294 & 0.000 \\
stateIndiana & 0.902 & 3.268 & 0.276 & 0.783 \\
stateIowa & -4.692 & 3.101 & -1.513 & 0.131 \\
stateKansas & -0.798 & 3.275 & -0.244 & 0.808 \\
stateMaine & -10.182 & 2.726 & -3.735 & 0.000 \\
stateMaryland & -20.244 & 2.998 & -6.753 & 0.000 \\
stateMassachusetts & -22.543 & 2.753 & -8.190 & 0.000 \\
stateMichigan & -6.635 & 2.576 & -2.576 & 0.010 \\
stateMinnesota & -10.250 & 2.684 & -3.819 & 0.000 \\
stateMissouri & 1.087 & 2.803 & 0.388 & 0.698 \\
stateMontana & 1.379 & 2.784 & 0.495 & 0.620 \\
stateNational & -7.935 & 2.546 & -3.117 & 0.002 \\
stateNebraska & -7.528 & 2.782 & -2.706 & 0.007 \\
stateNevada & -5.617 & 2.594 & -2.165 & 0.031 \\
stateNew Hampshire & -8.778 & 2.655 & -3.306 & 0.001 \\
stateNew Jersey & -15.189 & 3.577 & -4.246 & 0.000 \\
stateNew Mexico & -10.980 & 3.099 & -3.543 & 0.000 \\
stateNew York & -15.239 & 2.633 & -5.789 & 0.000 \\
stateNorth Carolina & -4.783 & 2.582 & -1.853 & 0.064 \\
stateNorth Dakota & 2.970 & 4.380 & 0.678 & 0.498 \\
stateOhio & -2.796 & 2.677 & -1.045 & 0.296 \\
stateOklahoma & 8.450 & 4.385 & 1.927 & 0.054 \\
stateOregon & -14.974 & 4.385 & -3.415 & 0.001 \\
statePennsylvania & -6.375 & 2.568 & -2.483 & 0.013 \\
stateRhode Island & -13.374 & 2.994 & -4.467 & 0.000 \\
stateSouth Carolina & -1.939 & 4.376 & -0.443 & 0.658 \\
stateSouth Dakota & 0.394 & 3.096 & 0.127 & 0.899 \\
stateTennessee & 3.624 & 4.378 & 0.828 & 0.408 \\
stateTexas & -3.825 & 2.681 & -1.427 & 0.154 \\
stateUtah & -3.243 & 4.385 & -0.740 & 0.460 \\
stateVermont & -23.452 & 3.581 & -6.549 & 0.000 \\
stateVirginia & -9.518 & 2.663 & -3.575 & 0.000 \\
stateWashington & -15.876 & 3.264 & -4.864 & 0.000 \\
stateWest Virginia & 8.265 & 4.379 & 1.887 & 0.059 \\
stateWisconsin & -6.444 & 2.571 & -2.506 & 0.012 \\
stateWyoming & 15.921 & 4.377 & 3.637 & 0.000 \\
transparency\_score & -0.646 & 0.088 & -7.383 & 0.000 \\
end\_date & 0.006 & 0.001 & 8.880 & 0.000 \\

\end{longtable}

\section{Diagnostic plots for the
model}\label{diagnostic-plots-for-the-model}

\centering{

\includegraphics{paper_files/figure-pdf/fig-diagnosis-1.pdf}

}

\caption{\label{fig-diagnosis}}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(car)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
Loading required package: carData
\end{verbatim}

\begin{verbatim}

Attaching package: 'car'
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:dplyr':

    recode
\end{verbatim}

\begin{verbatim}
The following object is masked from 'package:purrr':

    some
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{vif}\NormalTok{(regression\_model)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
                       GVIF Df GVIF^(1/(2*Df))
numeric_grade      1.294110  1        1.137590
sample_size        1.289750  1        1.135672
state              2.082151 44        1.008369
transparency_score 1.263558  1        1.124081
end_date           1.309491  1        1.144330
\end{verbatim}

@@

\subsection{Predict and Combine with Electroal College to
Predict}\label{predict-and-combine-with-electroal-college-to-predict}

\begin{longtable}[]{@{}lrrl@{}}

\caption{\label{tbl-prediction}Prediction for Trump}

\tabularnewline

\caption{Prediction for Trump by State}\tabularnewline
\toprule\noalign{}
State & Trump Predicted \% & Electoral Votes & Winner \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
State & Trump Predicted \% & Electoral Votes & Winner \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Alaska & 53.00 & 3 & Trump \\
Arizona & 47.62 & 11 & Harris \\
Arkansas & 56.60 & 6 & Trump \\
California & 34.39 & 55 & Harris \\
Colorado & 37.60 & 9 & Harris \\
Connecticut & 39.09 & 7 & Harris \\
Florida & 48.89 & 29 & Harris \\
Georgia & 47.71 & 16 & Harris \\
Idaho & 54.50 & 4 & Trump \\
Illinois & 36.37 & 20 & Harris \\
Indiana & 53.73 & 11 & Trump \\
Iowa & 46.68 & 6 & Harris \\
Kansas & 49.63 & 6 & Harris \\
Maine & 41.13 & 2 & Harris \\
Maryland & 32.88 & 10 & Harris \\
Massachusetts & 29.80 & 11 & Harris \\
Michigan & 45.92 & 15 & Harris \\
Minnesota & 42.40 & 10 & Harris \\
Missouri & 52.51 & 10 & Trump \\
Montana & 54.20 & 3 & Trump \\
Nebraska & 45.16 & 5 & Harris \\
Nevada & 47.00 & 6 & Harris \\
New Hampshire & 42.86 & 4 & Harris \\
New Jersey & 37.60 & 14 & Harris \\
New Mexico & 42.05 & 5 & Harris \\
New York & 37.45 & 29 & Harris \\
North Carolina & 47.98 & 16 & Harris \\
North Dakota & 54.00 & 3 & Trump \\
Ohio & 49.58 & 18 & Harris \\
Oklahoma & 58.70 & 7 & Trump \\
Oregon & 35.30 & 6 & Harris \\
Pennsylvania & 46.28 & 20 & Harris \\
Rhode Island & 39.12 & 4 & Harris \\
South Carolina & 50.60 & 9 & Trump \\
South Dakota & 52.18 & 3 & Trump \\
Tennessee & 55.30 & 11 & Trump \\
Texas & 48.51 & 38 & Harris \\
Utah & 47.00 & 6 & Harris \\
Vermont & 28.00 & 3 & Harris \\
Virginia & 43.22 & 13 & Harris \\
Washington & 36.33 & 12 & Harris \\
West Virginia & 59.30 & 5 & Trump \\
Wisconsin & 45.96 & 10 & Harris \\
Wyoming & 67.60 & 3 & Trump \\

\end{longtable}

@@

\section*{Appendix}\label{appendix}
\addcontentsline{toc}{section}{Appendix}

@@

@@

@@

@@
